Parsing Postfix log files

### 2008-07-30 doc/logparser-implementation.tex
Moved complications to their own subsection.

\subsubsection{Complications encountered}

XXX DUNNO IF THIS SECTION SHOULD BE HERE\@.  QUEUEID VS PID IS NOT TOO
IMPORTANT\@; CONNECTION REUSE COULD EASILY BE MOVED TO ADDITIONAL
COMPLICATIONS\@; RE-INJECTED MAILS SHOULD PROBABLY BE MOVED TO ADDITIONAL
COMPLICATIONS TOO\@.

\label{complications}

These complications were encountered early in the parser's implementation
and guided its design and development.

@@

\subsubsection{Additional complications}

\label{additional complications}

The complications described in this section are listed in the order in
which they were encountered during development of the parser.  Each of
these complications caused the parser to operate incorrectly, generating
either warning messages or leaving mails in the state table.  The frequency
of occurrence is much higher at the start of the list, with the first
complication occurring several orders of magnitude more frequently than the
last.  When deciding which problem to address next, the most common was
always chosen, as resolving the most common problem would yield the biggest
improvement in the parser, prune the greatest number of mails from
the state tables and error messages, and make the remaining problems more
apparent.

@@

>>>>

@@

\subsection{Complications encountered}

\label{additional complications}
\label{complications}

The complications described in this section are listed in the order in
which they were encountered during development of the parser.  Each of
these complications caused the parser to operate incorrectly, generating
either warning messages or leaving mails in the state table.  The frequency
of occurrence is much higher at the start of the list, with the first
complication occurring several orders of magnitude more frequently than the
last.  When deciding which problem to address next, the most common was
always chosen, as resolving the most common problem would yield the biggest
improvement in the parser, prune the greatest number of mails from the
state tables and error messages, and make the remaining problems more
apparent.  The first three complications were encountered early in the
parser's implementation and guided its design and development.

@@

\subsection{Summary}

XXX TO BE WRITTEN\@.
